\chapter{Beureg}
\label{ch:beureg}
\index{meal}
\index{spinach}
\index{feta}

\marginnote{
    \textbf{Makes 1 large pan} \\
    Prep time: 1 hour \\
    Cook time: 1 hour \\
    \vspace*{\baselineskip}

    \textbf{Ingredients for dough} \\
    3 cups all-purpose flour \\
    3/4 cup vegetable oil, Canola \\
    1/4 cup butter, melted \\
    1 tsp baking powder \\
    1 egg \\
    1 cup milk, room temperature \\
    \vspace*{\baselineskip}

    \textbf{Ingredients for filling} \\
    1 onion, diced \\
    142g fresh spinach or 1 packet frozen, thawed \\
    250g feta, grated \\
    2-3 eggs \\
    Milk \\
    \vspace*{\baselineskip}

    \textbf{Egg wash} \\
    1 egg \\
    Nigella or sesame seeds
}

\textit{Spinach and cheese pie}

Family member: Sybil

\begin{enumerate}
    \item In a large bowl, mix all the ingredients for the dough together until a dough forms. Cover the bowl with plastic wrap and keep aside.
    \item To make the filling, cook the onion with a some oil in a pan.
    \item Add the fresh or thawed spinach, and cook on medium heat.
    \item Pour the mix into a bowl. Once cool, add the grated feta, the eggs and a little bit of milk. Mix well using a fork.
    \item Divide the dough in 2 parts, and roll them out using a rolling pin. Use some flour if needed on the working surface.
    \item In a rectangular dish, place one half. Spread the filling on top. Cover with the second dough.
    \item For egg wash, whisk 1 egg yolk with a little bit of water in a bowl. Brush the egg wash onto the top and sprinkle with nigella or sesame seeds.
    \item Bake at 350\degree F on the top rack for about 1 hour.
\end{enumerate}

