\chapter{Cheureg}
\label{ch:cheureg}
\index{dessert}
\index{bread}
\index{Easter}
\textit{Easter bread}

Family member: Great Grandma

\marginnote[20pt]{\\
    \textbf{Makes 4-6 braids} \\
    Prep time: 5-6 hours \\
    Cook time: 30 minutes \\
    \vspace*{\baselineskip}

    6 eggs \\
    2 packets of traditional yeast \\
    2 tsp sugar \\
    1/2 tsp water \\
    10 cups all-purpose flour + 1/2 cup, Robin Hood \\
    Mahleb, ground \\
    2 cups of milk, lukewarm \\
    2 cups sugar \\
    1.5 cups of butter, melted \\
    Egg yolks, beaten for egg wash \\
}

% \newthought{}
% \bigskip

\begin{enumerate}
    \item In a large bowl, mix the flour, baking powder, mahleb and sugar.
    \item Add the oil and margarine. Add the milk accordingly.
    \item Shape into thin ropes, then into 2-inch circles.
    \item Place on baking sheet lined with parchment.
    \item In a small bowl, start yeast: place packets of yeast, 2 tsp sugar and water. Let for 15 minutes.
    \item In a large bowl, whisk the flour and mahlep. 
    \item Create a well in the dry ingredients and add the yeast mixture. Incorporate the flour into the yeast slowly.
    \item In a small bowl, beat the eggs slightly. Add them to the flour/yeast mixture above.
    \item In another bowl, add the sugar to the lukewarm milk and mix it. Add it to the flour/yeast/egg mixture and mix well.
    \item Slowly add the melted butter while mixing. Knead the dough until smooth.
    \item Cover the dough, and let proof for 3-4 hours in a bowl covered with plastic wrap.
    \item Punch down the dough, shape into braids. Cover with a clean towel and let rise for 1 hour. Brush the braids with egg wash.
    \item Bake at 350\degree F for about 30 minutes, sprinkle with sugar when cooled.
    If large, thick braids - on bottom rack.
    If small braids - on top rack.
\end{enumerate}