\chapter{Ham Quiche}
\label{ch:hamquiche}
\index{meat}
\index{meal}
\index{pie}
\index{brunch}

Family member: Aunt Joanne

\marginnote[20pt]{\\
    \textbf{Makes 1 quiche} \\
    Prep time: 30-45 minutes \\
    Cook time: 45 minutes \\
    \vspace*{\baselineskip}

    Pastry for one 9-inch piecrust, well chilled (Tenderflake Deep Dish pie crust) \\
    Margarine \\
    1 large onion, chopped (about 1 cup) \\
    1 tablespoon all purpose flour \\
    1/4 pound (120 grams) of Gruyere cheese \\
    1/4 pound (120 grams) of Swiss cheese \\
    1 slice of smoked ham \\
    3 large eggs \\
    1 cup half-and-half cream \\
}

% \newthought{}
% \bigskip

\begin{enumerate}
    \item Prepare a 9 inch piecrust, or take out the Tenderflake Deep Dish pie crust.
    \item In a small skillet over medium heat, melt 2 tablespoons of margarine. Cook the chopped union until tender, about 5 minutes, stirring occasionally. Once cooked, spread it evenly in the pie crust.
    \item Preheat oven to 400\degree F.
    \item Chop the smoked ham slice into little cubes.
    \item Shred both Gruyere and Swiss cheese. In medium bowl, toss the cheeses with flour.
    \item Mix in the cubed ham with the cheeses and spread them over the onion in the piecrust.
    \item Beat 3 eggs with 1 cup of half-and-half cream. Pour it over the shredded cheese and ham mix in piecrust.
    \item Bake for 10 minutes. Reduce the oven to 325\degree F and bake for 30 to 35 minutes longer until knife inserted in center comes out clean.
    \item Let the pie stand 10 minutes, then cut into wedges.
\end{enumerate}