\chapter{Mantuh Shahinian}
\label{ch:mantuhshahinian}
\index{meat}
\index{meal}
\index{pasta}
\index{yogurt}

\marginnote{
    \textbf{Makes 6-8~servings} \\
    Prep time: 30~minutes \\
    Cook time: 35-45~minutes \\
    \vspace*{\baselineskip}

    1.5~kg ground beef, lean \\
    2~onions, chopped \\
    Cinnamon, optional \\
    Salt and pepper \\
    3~garlic cloves, crushed \\
    1~kg Balkan Yogurt 6\% fat, Astro brand \\
    Canola oil \\
    500~g/2~packets of pasta Rigatoni
}

Family member: Sybil

\newthought{Sybil} remembers her Uncle Torkom, Nene Hermine's brother, would make this meal and serve it using a plate to scoop and serve the pasta! This was one of my favorite dishes when I stayed over Vasken's parents' house for dinner when we started dating. Great for a family dinner.

\begin{enumerate}
    \item In a hot pan, cook the onions in a little bit of canola oil until they are caramelized. In another pan, cook the ground beef in some oil. Season to taste with salt and pepper, and add cinnamon if desired. Once they are done, set the caramelized onions and meat aside to cool, keeping them separated.
    \item Meanwhile, prepare the pasta following the package instructions.
    \item Preheat oven to 350\degree F. In a bowl, mix the yogurt with the crushed garlic and a pinch of salt.
    \item In a large ovenproof dish, spread the pasta evenly. Layer the cooked meat on top, then the yogurt in one layer. Finish by adding the caramelized onion on top of the yogurt.
    \item Bake in the preheated oven for about 35-45~minutes.
\end{enumerate}
