\chapter{Pasta and Meat Sauce}
\label{ch:pastameatsauce}
\index{meat}
\index{meal}
\index{pasta}

\marginnote{
    \textbf{Makes 6-8~portions} \\
    Prep time: 30-45~minutes \\
    Cook time: 5~hours \\
    \vspace*{\baselineskip}

    2~tbsp olive oil \\
    1~finely chopped small onion \\
    1~garlic clove, crushed (optional) \\
    227~g (½~lb) of minced veal \\
    227~g (½~lb) of minced pork \\
    227~g (½~lb) of minced beef \\
    300~g Chianti Red Wine Rosette de Lyon dried sausage by Papille \\
    1~can (796~ml) Aylmer Diced Tomatoes with Italian Spices \\
    2~cans (156~ml) of Unico Tomato Paste \\
    1¼~cups of red wine \\
    2~tsp dried oregano \\
    Fresh basil \\
    1~tsp sugar \\
    Salt \\
    Pepper \\
    Pasta of your choice
}

Family member: Aunt Joanne

\begin{enumerate}
    \item Slice the dried sausage and put it aside.
    \item Heat the olive oil in a skillet and gently cook the onion and garlic, stirring for 10~minutes until softened.
    \item Add the minced veal, pork and beef and cook until they change colour, stirring constantly and breaking up the meat. Stir in the dried sausage.
    \item Purée the diced tomatoes in a blender and pour into a cooking pot. You can also leave them diced as is.
    \item Mix each can of tomato paste in a cup of water and add them to the cooking pot.
    \item Add 1-¼~cups of red wine. Add sugar, salt and pepper.
    \item Stir in the meat/onion/garlic mixture into the pot.
    \item Add dried oregano and fresh shredded basil and bring to a boil while stirring.
    \item Cover and lower the heat to a gentle simmer for 3~to 4~hours, stirring occasionally.
\end{enumerate}

AJ usually prepares a larger quantity in a very big pot and freezes the sauce in many containers.
