\chapter{Souloukefteh}
\label{ch:souloukefteh}
\index{meal}
\index{meat}
\index{soup}

\marginnote{
    \textbf{Makes 4~servings} \\
    Prep time: \\
    Cook time: 3½-4~hours \\
    \vspace*{\baselineskip}

    \textbf{Ingredients for stock} \\
    1~beef shank or 2~veal shanks (about 454~g/1~lb) \\
    1~large yellow onion \\
    2~bay leaves \\
    8-10~cups of water \\
    1~tsp tomato paste \\
    \vspace*{\baselineskip}

    \textbf{Ingredients for soup} \\
    Reserved stock \\
    454~g (1~lb) ground beef \\
    ½~large yellow onion \\
    ¼~cup rice, Calrose \\
    ½~cup parsley, chopped \\
    1~egg \\
    Salt \& pepper to taste
    3~white or Russet potatoes, cubed \\
    Carrots, chopped (optional) \\
    ¼~cup rice, Calrose (or orzo)
}

\textit{Soupe boulettes de viande}

Family member: Metzma Lucie

\begin{enumerate}
    \item Add all the ingredients for the stock except the tomato paste in a large pot and bring it to a boil. Cook for 2.5~hours.
    \item Remove the shank, take off the meat and add it to the stock. Remove the onion dd the tomato paste and mix.
    \item In a bowl, grate the onion and mix it with the meat, rice, parsley and egg. Add salt and pepper and let stand for about 15~minutes.
    \item Form 1.5-inch balls of the meat mixture while bringing the stock to a boil.
    \item Add the meatballs and reserved ¼~cup rice (or orzo). Reduce to a simmer.
    \item After 15~minutes, add the potatoes (and carrots if using) and continue cooking for 30~minutes to 1~hour.
\end{enumerate}
