\chapter{Roasted Beet Salad with Ricotta}
\label{ch:roasted-beet-salad}
\index{salad}
\index{beet}
\index{ricotta}

\marginnote{
    \textbf{Makes 4-6~servings} \\
    Prep time: 20~minutes \\
    Cook time: 45~minutes \\
    \vspace*{\baselineskip}

    1~kg red and yellow beets, peeled and sliced \\
    1~grapefruit and 1~orange, cut into supremes and keep 1~tbsp juice of each \\
    2~tsp lemon juice \\
    1~small shallot, minced \\
    1~tbsp honey \\
    2~tbsp parsley, chopped \\
    75~g-100~g ricotta (or goat cheese) \\
    55~g pistachios, toasted and chopped \\
    Olive oil \\
    Rosemary, fresh \\
    Salt \& pepper to taste
}

Family member: Elsa \& Vaski

\begin{enumerate}
    \item In a large bowl, toss beets with olive oil, rosemary, salt and pepper. If using yellow and red beets, toss separately. Place in aluminum foil pouches, onto a baking sheet and roast about 45~minutes at 400\degree F, or until you can easily poked them with a knife. Cool.
    \item Make vinaigrette: Take ½~the pistachios and grind into a coarse powder using the mortar and pestle. In a small bowl, combine the ground pistachios with the orange and grapefruit juices, lemon juice, shallot, honey, parsley and about 3~tbsp of olive oil. Whisk until well combined. Place the different coloured beets in 2~different bowls and toss them each with the vinaigrette. Season with salt and pepper.
    \item On a pretty plate, spread some of the ricotta or goat cheese and place the beets in the middle. Place the supremes of citrus and drizzle some of the vinaigrette. Add chopped parsley, chopped pistachios and some dollops of ricotta and goat cheese.
\end{enumerate}

Can keep in the fridge for a little while before serving.
Really good next to a grilled meat or lamb dish with potatoes.

