\chapter{Lasagna}
\label{ch:lasagna}
\index{meal}
\index{pasta}
\index{meat}
\index{cheese}

\marginnote{
    \textbf{Makes 8+ servings} \\
    Prep time: 30-45 minutes \\
    Cook time: 35 minutes \\
    \vspace*{\baselineskip}

    \textbf{One recipe of Meat sauce, page~\pageref{ch:meatsauce}} \\
    \vspace*{\baselineskip}

    454 g (1 pkg) Ricotta cheese \\
    285 g (1 pkg) frozen chopped spinach, thawed and drained \\
    2 eggs, lightly beaten \\
    500 g lasagna noodles, Primo (around 12 sheets) \\
    1 jar of Catelli Garden Select Tomato \& Basil Pasta Sauce (640ml) \\
    Shredded mozzarella cheese \\
    Grated Pecorino cheese, Chelmos Greek or mitzithra
}

Family member: Mom

\newthought{Lasagna} was a comforting dinner Mom used to make on Sundays. We would get yelled at for eating the top layer of pieces (: You can omit the ricotta \& spinach layer if you want and make it a very meat and cheesy lasagna!

\begin{enumerate}
    \item Preheat oven to 350\degree F and grease a 9X13-inch ovenproof dish with Pam spray.
    \item Cook the lasagna noodles according to the package instructions. Once done, set aside.
    \item In a bowl, mix the ricotta cheese, eggs and spinach.
    \item Spread a thin layer of Garden Select Pasta Sauce, approximately 4 tbsp, in the bottom of the ovenproof dish. Top with 4 lasagna sheets or more, enough to cover the whole bottom of the dish.
    \item Top with the prepared meat sauce. Add another 2 tbsp of the Pasta Sauce on top and sprinkle with 2 tbsp of Pecorino cheese.
    \item Top with the lasagna sheets. On top, spread all of the prepared spinach mixture and top with more sheets of lasagna.
    \item Top with more meat sauce, 2 tbsp of Pasta Sauce on top and another 2 tbsp of Pecorino cheese.
    \item Top with lasagna noodles and remaining meat sauce. Sprinkle enough shredded mozzarella to cover all the meat sauce and some more of the Pecorino cheese.
    \item Bake for 35-45 minutes, or until the top is golden and bubbly and the corners are crusty. Let cool before cutting into slices! Enjoy :)
\end{enumerate}

Leave the frozen spinach on the counter for a few hours to defrost. Squeeze out the liquid as much as you can before adding it to the egg and ricotta.

