\chapter{Mavromatika}
\label{ch:mavromatika}
\index{meal}
\index{spinach}
\index{beans}
\textit{Spinach stew with black eye peas}

Family member: Mom

\marginnote[20pt]{\\
    \textbf{Makes 6 servings} \\
    Prep time: 20 minutes \\
    Cook time: 2 hours + overnight soaking \\
    \vspace*{\baselineskip}

    1/2 mug of black eyed peas, dried (or 1/2 cup) \\
    1 medium onion, grated \\
    1/2 - 1 can tomato sauce, Hunt’s (213 ml) \\
    2 bags of spinach, fresh \\
    Olive oil \\
}

% \newthought{}
% \bigskip

\begin{enumerate}
    \item Soak black eyed peas in water overnight.
    \item The next day, drain the water. Put them in a pot with water and bring them to a simmer. Cook for about 20-30 minutes until almost done and strain.
    \item In a large pot, bring water to a boil. Add spinach and cook until soft, for about 15 minutes. Strain the spinach on top of the black eyes peas.
    \item Heat a medium pot and add oil. Cook onion until softened, then add the beans and the spinach. Add the tomato sauce, 2 cans of water, salt and pepper.
    \item Simmer until reduced and thickened. During cooking, you can add more water if thickens too much, to get desired consistency.
    \item After about 1 hour to 1 hour and a half, check the beans for doneness, then turn off heat and let cool.
\end{enumerate}

\marginnote{
    To speed things up, I would use 1 can of black eyed peas and skip Steps 1 and 2. It is quicker to make and would take a total of 45 min to cook.
    Also really good with, you guessed it, a slice of village bread and a large piece of feta!
}