\chapter{Melomakarona}
\label{ch:melomakarona}
\index{dessert}
\index{cookies}
\index{walnut}

\marginnote{
    \textbf{Makes ? cookies} \\
    Prep time: ? minutes \\
    Cook time: 30~minutes \\
    \vspace*{\baselineskip}

    \textbf{Ingredients for cake} \\
    7~cups all purpose flour, Five Roses
    3~cups vegetable oil
    1/2~cup sugar \\
    1/2~cup orange juice, freshly squeezed \\
    1/2~cup beer \\
    2~tsp cinnamon \\
    1~tsp cloves \\
    3~tsp baking powder \\
    \vspace*{\baselineskip}
    
    \textbf{Ingredients for syrup and decoration} \\
    Greek honey \\
    1/2~cup sugar \\
    1/2~cup water \\
    Walnuts, crushed
}

\textit{Honey cookies with walnuts and syrup}

Family member: Grandma Eleni

\begin{enumerate}
    \item In a large bowl, mix all the ingredients for the melomakarona. Start with 6~cups flour, and add more to get texture needed to shape.
    \item Place the shapes melomakarona on a baking sheet. Bake at 350\degree F for about 30~minutes or until slightly golden.
    \item Once the cookies are done and have a golden colour, remove from the oven. Let the cookies cool. 
    \item To make the syrup, put the ingredients in a medium pot and mix. Heat until it simmers and let it boil for 5~minutes. Remove from the heat.
    \item Once the cookies have cooled, put the warm syrup in a large bowl. Dip the cookies one by one, on both sides with a fork in the syrup. Place them on a cooling rack for excess syrup to drip
    \item Decorate with crushed walnuts before storing them in a large Tupperware.
\end{enumerate}

% TODO: koupa
Koupa used by grandma for this recipe is equivalent to ? ml
